%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer II} % Job title
    {JP Morgan Chase \& Co.} % Organization
    {Bangalore} % Location
    {July 2021 - August 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Specializing in backend engineering, infrastructure architecture, and finance domain expertise.}
        \item {\textbf{Led a team of 5} engineers to architect, develop and design the standardization of payment settlement clearing processes across corporate investment banks.}
        \item {Successfully delivered major projects, such as \textbf{BACS and SIC CHF}, and implemented \textbf{ISO 20022 standards} for partner banks and clearing houses. Possess deep expertise in transaction types and financial messages, including \textbf{Direct Debit, Direct Credit, and PACS}.}
        \item {Played a pivotal role in the successful migration of a legacy project to the latest tech stack, resulting in a \textbf{5x increase in transaction processing speed}.}
        \item {\textbf{Fixed a critical log4j data leak vulnerability} in December 2021, delivering the fix to production across all connectors within 48 hours.}
        \item {End-to-end sprint management for product release involving sprint planning, demos, participation in retrospective meetings till sprint closure.}
        % \item{\textbf{Tech stack:} Java, Spring, Hibernate, Kubernetes, Kafka, Oracle SQL database}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Harman} % Organization
    {Delhi} % Location
    {August 2019 - July 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of the Hoffman Roche team, developing health diagnostics IoT devices that collect essential data for disease diagnosis and analysis.}
        \item {Performed POC assessments to evaluate and select HIPAA-compliant tools, libraries, and frameworks.}
        \item {Contributed to the finalization of API architecture to ensure the capacity to handle up to \textbf{10k concurrent requests}.}
        \item {Detected and \textbf{mitigated security vulnerabilities} introduced through external libraries, using tools like Raven scan for generating and analyzing detailed reports.}
        \item {Created data pipelines to gather information from IoT devices and prepare it for daily report generation and consumption by the ML team.}
        \item {Designed and implemented robust authorization and authentication systems with \textbf{OAuth2}.}
        % \item{\textbf{Tech stack:} Java, Spring boot, Redis, Postgres, MongoDB}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Nucleus Software} % Organization
    {Delhi} % Location
    {July 2016 - July 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Started my journey as Associate Software Engineer at one of the leading provider of lending and transaction banking software for banks and financial institutions.}
        \item {Optimized table structures to reduce database hits and shared these insights with other teams to \textbf{improve application performance by 3x}.}
        \item {Created a modular statement of account reporting system with multiple file output options.}
        \item {Designed and implemented API to allow bankers to select custom Loan disbursement \& repayment options for their customers.}
        \item {Engineered web connectors to help loan management service fetch important details from customer data service.}
        \item {Added functionality to add secondary account \& its roles and authorisation to an active loan.}
        % \item {Implemented a flow to do KYC from multiple government identities.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}